Automated Timed Temporal Verification

### 2022-03-29 paper/tv.tex
m

\begin{figure}[ht]
      \vspace{0mm}
\begin{lstlisting}[columns=fullflexible]
void addSugar(int n)
/* requires n>0,  _^*.Cup */
/* ensures  t>=n, Sugar # t */
{ if n == 0 then event[Sugar] 
  else {
    timeout (oneSugar(), 1);
    addSugar (n-1);}}

void makeCoffee (int n)
/* requires n>0, emp */
/* ensures  t<5/\t>=n/\t1<3, 
 Cup.(Sugar#t).(Coffee#t1).Done */
{ event[Cup];
  deadline (getSugar(n), 5);
  deadline (event[Coffee], 3);
  event[Done];}

void main () 
/* requires true, emp */
/* ensures  t<8, (_^*.Done)#t */
{ makeCoffee(3);}
// make coffee with 3 lumps of sugar

>>>>

\begin{figure}[ht]
      \vspace{0mm}
\begin{lstlisting}[columns=fullflexible]
void addSugar(int n)
/* requires n>0,  _^*.Cup 
   ensures  t>=n, Sugar # t */
{ if n == 0 then event[Sugar] 
  else {
    timeout (oneSugar(), 1);
    addSugar (n-1);}}

void makeCoffee (int n)
/* requires n>0, emp 
 ensures  t<5/\t>=n/\t1<3, 
 Cup.(Sugar#t).(Coffee#t1).Done */
{ event[Cup];
  deadline (addSugar(n), 5);
  deadline (event[Coffee], 3);
  event[Done];}

void main () 
/* requires true, emp 
 ensures  t<8, (_^*.Done)#t */
{ makeCoffee(3);}
// make coffee with 3 lumps of sugar
